Radio Emission from Red-Giant Hot Jupiters

### 2015-09-18 ms.tex
sub photon
Added grant info
Fixed affiliation error

\affil{$^8$Center for Computational Relativity and Gravitation, Department of Mathematics, Rochester Institute of Technology, Rochester, NY 14623}

@@

The source rate is obtained by counting the number of photons whose energy exceeds the ionization energy of Hydrogen ($E_{\rm Rydberg} = 13.6$~eV, %where Ry is the Rydberg constant, 
or $\lambda = 91.2\rm~nm$), which is approximately given by dividing the X-ray accretion luminosity by the characteristic photon energy produced:
%%%%%%%%%
\begin{equation}
\dot{N}_X \sim \frac{L_{\rm acc}}{k_B T_{\rm acc}} \, ,
\end{equation}
%%%%%%%%%
where $k_B$ is Boltzmann's constant.
As a result, 
%%%%%%%%%
\begin{eqnarray}
\dot{N}_X \sim  
  \left\{
    \begin{array}{ll}
      2 \times 10^{35} \;  {\rm sec^{-1}} & \;\;\;(M_p = M_J) \\
      3 \times 10^{37} \; {\rm sec^{-1}} & \;\;\;(M_p = 10 M_J)
    \end{array}. 
  \right.
\end{eqnarray}
%%%%%%%%%
For the accretion disks of large planets, however, the characteristic photon energy is so high (equation (\ref{eq:Tacc})) that the released energetic electrons may also ionize other atoms in the vicinity; the cross section of hydrogen for electrons is $\sim 4\times 10^{-17} {\rm cm}^2$  \citep{fite1958} and thus about 60\% of the released electrons will be used to ionize other atoms within a distance of $2R_J$. 
Photons with energy $E{\rm photon}$ have potential to ionize $E_{\rm photon}/E_{\rm Rydberg}$ times. 
To take this into account, we also consider replacing the source term $\dot N_X$ in equation (\ref{eq:equilibrium}) by 
%%%%%%%%%
\begin{equation}
\dot{N}_X \rightarrow \dot{N}_X \left[ 1 + \xi \left( \frac{E_{\rm photon}}{E_{\rm Rydberg}} - 1 \right) \right] 
\end{equation}
%%%%%%%%%
where the $\xi$ is a fudge factor to represent the efficiency of this reaction. \memoDS{Does the above argument imply that $\xi \sim 0.6$?  Should we think of it as an $N$-Rydberg photon, if absorbed, leads to 1 $N-1$-Rydberg electron, which produces 0.6 $N-2$-Rydberg electrons, $0.6^2$ $N-3$-Rydberg electrons, ... and $0.6^{N-1}$ 0-Rydberg electrons, so in the end we have $1 + 0.6 + 0.6^2 + ... + 0.6^{N-1} \sim 2.5$ electrons?}
% N - power - 1 = energy of electrons
% N - (N-1) - 1 = 0-Rydberg electron

@@

YF is supported from the Grant-in-Aid No. 25887024 by the Japan Society for the Promotion of Science.
DSS gratefully acknowledges support from a fellowship from the AMIAS group.
We thank David Hogg for encouraging us to pursue calculations of exoplanetary radio emission.
NM acknowledges support from [???]. 
YF greatly acknowledges insightful and helpful discussions with Tomoki Kimura and Hiroki Harakawa. 
The portion of this research for which TM is responsible was performed under a National Research 
Council Research Associateship Award at the Naval Research Laboratory (NRL).
Basic research in radio astronomy at NRL is supported by 6.1 Base funding.

>>>>

\affil{$^8$Center for Computational Relativity and Gravitation, Rochester Institute of Technology, Rochester, NY 14623}

@@

The source rate is obtained by counting the number of photons whose energy exceeds the ionization energy of Hydrogen ($E_{\rm Rydberg} = 13.6$~eV, %where Ry is the Rydberg constant, 
or $\lambda = 91.2\rm~nm$), which is approximately given by dividing the X-ray accretion luminosity by the characteristic photon energy produced:
%%%%%%%%%
\begin{equation}
\dot{N}_X \sim \frac{L_{\rm acc}}{k_B T_{\rm acc}} \, ,
\end{equation}
%%%%%%%%%
where $k_B$ is Boltzmann's constant.
As a result, 
%%%%%%%%%
\begin{eqnarray}
\dot{N}_X \sim  
  \left\{
    \begin{array}{ll}
      2 \times 10^{35} \;  {\rm sec^{-1}} & \;\;\;(M_p = M_J) \\
      3 \times 10^{37} \; {\rm sec^{-1}} & \;\;\;(M_p = 10 M_J)
    \end{array}. 
  \right.
\end{eqnarray}
%%%%%%%%%
For the accretion disks of large planets, however, the characteristic photon energy is so high (equation (\ref{eq:Tacc})) that the released energetic electrons may also ionize other atoms in the vicinity; the cross section of hydrogen for electrons is $\sim 4\times 10^{-17} {\rm cm}^2$  \citep{fite1958} and thus about 60\% of the released electrons will be used to ionize other atoms within a distance of $2R_J$. 
Photons with energy $E_{\rm photon}$ have potential to ionize $E_{\rm photon}/E_{\rm Rydberg}$ times. 
To take this into account, we also consider replacing the source term $\dot N_X$ in equation (\ref{eq:equilibrium}) by 
%%%%%%%%%
\begin{equation}
\dot{N}_X \rightarrow \dot{N}_X \left[ 1 + \xi \left( \frac{E_{\rm photon}}{E_{\rm Rydberg}} - 1 \right) \right] 
\end{equation}
%%%%%%%%%
where the $\xi$ is a fudge factor to represent the efficiency of this reaction. \memoDS{Does the above argument imply that $\xi \sim 0.6$?  Should we think of it as an $N$-Rydberg photon, if absorbed, leads to 1 $N-1$-Rydberg electron, which produces 0.6 $N-2$-Rydberg electrons, $0.6^2$ $N-3$-Rydberg electrons, ... and $0.6^{N-1}$ 0-Rydberg electrons, so in the end we have $1 + 0.6 + 0.6^2 + ... + 0.6^{N-1} \sim 2.5$ electrons?}
% N - power - 1 = energy of electrons
% N - (N-1) - 1 = 0-Rydberg electron

@@

YF is supported from the Grant-in-Aid No. 25887024 by the Japan Society for the Promotion of Science.
DSS gratefully acknowledges support from a fellowship from the AMIAS group. JN acknowledges support from NASA grant HST AR-12146.04-A and NSF grant AST-1102738.
We thank David Hogg for encouraging us to pursue calculations of exoplanetary radio emission.
NM acknowledges support from [???]. 
YF greatly acknowledges insightful and helpful discussions with Tomoki Kimura and Hiroki Harakawa. 
The portion of this research for which TM is responsible was performed under a National Research 
Council Research Associateship Award at the Naval Research Laboratory (NRL).
Basic research in radio astronomy at NRL is supported by 6.1 Base funding.
